Sharing displays and data from vision science research with Databrary

### 2015-05-07 vss-15/poster_landscape.tex
Change styling and minor edits to fit in space

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Privacy \& Security}{name=privacy,column=0,row=1, below=problem}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      Videos may contain identifiable information such as faces, voices, and images of places. 
      Databrary ensures that identifiable information can be shared in two ways:
      \begin{itemize}
      \item{\bf{Restricting Access}}

      Only those with independent researcher status at an institution may be granted authorized investigator status.
      Applicants promise to uphold ethical principles and sign an access agreement, which must be co-signed by their institution.

      \item{\bf{Securing Permission to Share}}

      Identifiable data may only be shared if participants have given permission.
      Databrary has developed a release template for obtaining informed consent for sharing identifiable data.
      The Databrary release template may be adapted for specific research protocols.

      \end{itemize}
  }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{What Can Be Shared}{name=shared,column=1,row=0}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    Databrary can house video, audio, PDF, spreadsheet, image, and text-based files along with associated metadata and annotations.
    Video files are transcoded into standard, HTML5-compatible formats, currently H.264+AAC in MP4. Databrary stores other data in native formats (e.g., .doc, .docx, .xls, .xlsx, .txt, .csv, .pdf, .jpg, .png).
  }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Technology Stack}{name=stack,column=0,below=privacy}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    Databrary is built on a PostreSQL database using the Scala Play framework and JavaScript.
    Data are preserved indefinitely in a secure data storage facility at NYU managed by central IT. 
    There is no cost to use the system; a sustainability model is under development.
    All code is hosted on GitHub.
  }

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Privacy \& Security}{name=privacy,column=0,row=1, below=problem}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      Videos may contain identifiable information such as faces, voices, and images of places. 
      Databrary ensures that identifiable information can be shared in two ways:
      \begin{description}
      \item[Restricting Access:]
      Only those with independent researcher status at an institution may be granted authorized investigator status.
      Applicants promise to uphold ethical principles and sign an access agreement, which must be co-signed by their institution.

      \item[Securing Permission to Share:]
      Identifiable data may only be shared if participants have given permission.
      Databrary has developed a release template for obtaining informed consent for sharing identifiable data.
      The Databrary release template may be adapted for specific research protocols.

      \end{description}
  }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% N.B.: this section is currently obscured by splash
  \headerbox{What Can Be Shared}{name=shared,column=1,row=0}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    Databrary can house video, audio, PDF, spreadsheet, image, and text-based files along with associated metadata and annotations.
    Video files are transcoded into standard, HTML5-compatible formats, currently H.264+AAC in MP4. Databrary stores other data in native formats (e.g., .doc, .docx, .xls, .xlsx, .txt, .csv, .pdf, .jpg, .png).
  }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Technology Stack}{name=stack,column=0,below=privacy}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    Databrary is built on PostreSQL using the Scala Play framework and AngularJS.
    Data are preserved indefinitely in a secure data storage facility at NYU. 
    There is no cost to use the system; a sustainability model is under development.
    All code is GPL on GitHub.
  }
